---
title: "A text analysis of The Lonely Island's lyrics"
author: "Arthur Azevedo"
date: "12/06/2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidytext)
library(tidyverse)
```

# First things first
_"If you are under 30 and you're totally cool, then you absolutely know these guys"_  
The very first sentence of the first song in the third studio album by _The Lonely Island_ (TLI) did find me under 30 and now 6 years later I'm stil totally cool. With the newest album finally out i had to that a look, and __why not__ thake a look in the old songs too.  

So... let's get the data.

## Extracting the data
I used the [geniusr](https://github.com/ewenme/geniusr) package to extract all lyrics from all TLI. You can find the script [here](https://github.com/arzevedo/Text_Mining/blob/master/The%20Lonely%20Island/the_lonely_island_lyrics_scrap.R) with you want to do it yourself, but you will have to make a genius account to use their API.
Anyway, i scraped the hole thing into a .csv file: 
```{r Loading, echo=TRUE, message=FALSE}
tli_lyrics <- read_csv("https://raw.githubusercontent.com/arzevedo/Text_Mining/master/The%20Lonely%20Island/the_lonely_island_lyrics.csv")
```
```{r some function bt D.Rob, include=FALSE}
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}


#' @rdname reorder_within
#' @export
scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}


#' @rdname reorder_within
#' @export
scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

## _"There's no way I’ll let my kids listen to it"_ 

The first thing that I'll do is to look at the most frequent words, let's see per Album.
```{r part1, message=FALSE, fig.width=8}
tli_lyrics_words <- tli_lyrics %>% 
  unnest_tokens(word, line) %>% 
  mutate(album_name = factor(album_name,
                             levels = c("Incredibad", "Turtleneck and Chain",
                                        "The Wack Album", "Popstar: Never Stop Never Stopping",
                                        "The Unauthorized Bash Brothers Experience", NA)))


tli_lyrics_words %>% 
  filter(!word %in% stop_words$word) %>% 
  group_by(album_name) %>% 
  filter(!is.na(album_name)) %>% 
  count(word, sort = TRUE) %>% 
  top_n(10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(word, n, album_name)) %>% 
  ggplot(aes(x = word, y = n))+
  geom_col()+
  labs(x = NULL, y = "Count", caption = "Viz: @RiversArthur",
       title = "No Homo")+
  scale_x_reordered()+
  coord_flip()+
  facet_wrap(~album_name, scales = "free_y")+
  theme_minimal()

```  

As I thought! lots of _boss_, _jizz_ and _pants_ in the first one. Well, a lot of f*** words in the popstar, and probabily mark and josé are the so called bash brothers from the latest album.  
4
```{r TF-IDF, fig.width=8}
tli_lyrics_words_per_album <- tli_lyrics_words %>% 
  count(album_name, word, sort = TRUE) %>% 
  ungroup()

total_words <- tli_lyrics_words_per_album %>% 
  group_by(album_name) %>% 
  summarise(total = sum(n))

tli_lyrics_words_per_album <- left_join(tli_lyrics_words_per_album, total_words)

tli_lyrics_words_per_album <- tli_lyrics_words_per_album %>%
  bind_tf_idf(word, album_name, n) %>% 
  filter(album_name != "NA")

tli_lyrics_words_per_album %>% 
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(album_name) %>%
  top_n(10) %>% 
  ungroup %>% 
  ggplot(aes(reorder_within(word, tf_idf, album_name), tf_idf)) +
  geom_col(show.legend = FALSE, aes(fill = album_name))+
  facet_wrap(~album_name, scales = "free_y") + 
  coord_flip()+
  scale_x_reordered()+ scale_y_continuous(labels = c("Less important words\n in each album",
                                                     "Important words\n in each album"),
                                          breaks = c(0.001,.023))+
  theme_minimal()+theme(legend.position = "none")+
  labs(caption = "Viz: @RiversArthur",
       x = NULL, y = NULL, title = "Highest tf-idf words in each of TLI's album")+
  theme(strip.text = element_text(size = 8),
        panel.grid.major = element_blank(), panel.grid = element_blank(),
        axis.text.y = element_text(size = 10))

```
